Review and comparison of tools for managing X.509 certificates and keys

### 2016-12-02 TEX/draft.tex
Changed itemized list into fluent text in Specifications

\textit{Yes} means that the tool supports signing of certificate signing request. \textit{No} if it does not support signing of certificate signing requests.

@@

\textit{Yes} - Possibility of choosing how long the certificate will be valid. Done by certificate authority. \textit{No} - If there is no option to change how long the certificate will be valid, so the duration is a fixed ammount.

@@

\begin{itemize}
 \item \textit{Yes} - possibility of setting a subject alternative name for certificate. It can be DNS name or IP address.
 \item \textit{No} - not possible to choose any subject alternative name.
\end{itemize}

\paragraph{Support for Cryptographic Service Provider}
\begin{itemize}
 \item \textit{Yes} - if there is option to change a cryptographic service provider. 
 \item \textit{No} - the cryptographic service provider canot be changed.
\end{itemize}

>>>>

\textit{Yes} means that the tool supports signing of certificate signing request. \textit{No} if it does not.

@@

\textit{Yes} if there is possibility of choosing how long the certificate will be valid. Done by certificate authority. \textit{No} If there is not such an  option, so the duration is a fixed ammount.

@@

\textit{Yes} means a  possibility of setting a subject alternative name for certificate. It can be DNS name or IP address. \textit{No} if there is no option to change any alternative name.

\paragraph{Support for Cryptographic Service Provider}
\textit{Yes} if there is option to change a cryptographic service provider. \textit{No} means that the cryptographic service provider canot be changed.
